---
title: "Initial Korean covid 19"
author: "Onalee Garusinghe"
date: "9/26/24"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
kRdata <- kRdata %>%
mutate(across(where(is.character), as.factor))

```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 2020
### This data was retrieved from a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Your Question - Is dying independent of sex?






## Graphical results - use ggplot commands to do this  



  




```{r}
barchartGC(~result + Sex,data=kRdata)
barchartGC(~result + Sex,data=kRdata, type="percent")

```
   
      The majority of people who were alive were female, at about 55%, while the rest were males, about 45%. However, out of the population that died, nearly 65% were male while 45% were female. This means there was a significant difference between the amount of males that died and the amount of females that died, males being the  majority, as they nearly doubled the amount of dead females.
  
  
## Numerical results

```{r}
table1 <- xtabs(~result + Sex, data=kRdata)
rowPerc(table1)
colPerc(table1)
```

  From the data, we can see that the majority of the alive population were Female, with a ratio of 56:44. However, of the dead population, the majority were males, with a ratio of 36:64. 3% of the male population were dead while 1.4% of the female population were dead, showing that the male population more than doubled the female population of dead people. 

## Inferential results 

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

  The Null results expected that the percentage of dead males and females compared to alive males and females would be equal. However, the observed counts showed that men nearly doubled the percentage of female dead population. The odds ratio of females dying to males dying is 2:3, showing that men are more likely to die than females.

## Conclusions

